An application of Graph Theory to MDAO problem formulation

### 2012-10-02 problem_formulation.tex
breaking things up

\section{Graph Based Problem Formulation Using XDSM}
    \subsection{Formulation Graph Syntax}
    Rather than start with an adjacency, we chose to work directly with a directed cyclic graph to develop a syntax for the FPF. 
    \begin{itemize}
        \item Specify analyses
        \item Connections between analyses 
            \begin{itemize}
                \item local variables
                \item global variables? Use "fake" node that broadcasts out to the rest of the graph? 
            \end{itemize}
        \item Cycles indicate coupling
        \item Cycles for design variables->objectives/constraints
        \item Objectives/constraints are just outputs? Special nodes? 
        \item Residuals are just outputs? Special nodes? 
        \item Parameters are just input nodes that are not design variables (use identifies these)
        \item FPF no solvers/optimizers anywhere in it
    \end{itemize}

    \subsection{Solution Graph Syntax}
    What is the difference between a problem formulation and a problem solution method? Convert from a cyclic graph, to an acyclic graph
    \begin{itemize}
        \item cycles indicate convergence loops or design varaible loops
        \item Problem can't be solved until all loops are *removed* by adding in solvers/optimizers
        \item *special* nodes for solvers and optimizers that *break* loops (from an algorithmic point of view)
        \item FPF represents the minimal amount of information necessary to define a problem
        \item Any solution path grows the graph complexity by adding edges and nodes (or possibly have an empty solution graph, which you build up 
        as you remove edges from problem formulation graph?)
    \end{itemize}

>>>>

\input{graph_syntax}
